### 2021-05-25 README.Rmd
got equation numbering and in-text references working using pandoc-crossref

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Title of your paper goes here"
```

@@

This repository contains the data and code for our paper:

> Authors, (YYYY).
> *`r Title`*.
> Name of journal/book <https://doi.org/xxx/xxx>

<!-- Our pre-print is online here: -->

<!-- > Authors, (YYYY). *`r Title`*. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx> -->

### How to cite

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`).
> *Compendium of R code and data for `r Title`*.
> Accessed `r format(Sys.Date(), "%d %b %Y")`.
> Online at <https://doi.org/xxx/xxx>

## How to run in your browser or download and run locally

@@

<!-- The simplest way to explore the text, code and data is to click on [binder](https://mybinder.org/v2/gh/BrunaLab/HeliconiaDemography/master?urlpath=rstudio) to open an instance of RStudio in your browser, which will have the compendium files ready to work with. -->

<!-- Binder uses rocker-project.org Docker images to ensure a consistent and reproducible computational environment. -->

<!-- These Docker images can also be used locally. -->

@@

-   Open the `.Rproj` file in RStudio
-   Install the `renv` package if it's not already installed and run `renv::restore()` to install all package dependencies. (I'm not actually sure that this step is necessar. Should auto-load because of .Rprofile.)
-   Run `targets::tar_make()` to run all code and produce all outputs.

### Licenses

<!-- **Text and figures :** [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/) -->

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

@@

This repository contains the data and code for a manuscript written for submission to Global Change Biology tentatively titled: "Delayed effects of climate on vital rates leads to demographic divergence in Amazonian forest fragments"

## How to run

@@

@@

-   Open the project in RStudio by double-clicking the `HeliconiaDemography.Rproj` file.
-   Install the [`renv` package](https://rstudio.github.io/renv/articles/renv.html) if it's not already installed and run `renv::restore()` to install all package dependencies.
-   Install the [`targets` package](https://docs.ropensci.org/targets/).
-   Run `targets::tar_make()` from the R console to run all code and produce all outputs.

## Notes

-   Numbering of and in-text references to equations in `paper.Rmd` is handled by [`pandoc-crossref`](https://github.com/lierdakil/pandoc-crossref), which may not be part of the standard RStudio pandoc installation. You might need to install it for the main text to knit correctly to Word.

<!--
### Licenses
-->
<!-- **Text and figures :** [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/) -->
